Name

### 2020-12-02 reviewer-response/reviewerX-response.tex

%@TheDoctorRAB
\documentclass[11pt,a4paper]{article} 
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in, bmargin=1in]{geometry} 
\usepackage{setspace} 
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage[yyyymmdd]{datetime}
\usepackage{fixltx2e}
\renewcommand{\dateseparator}{.}
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{times}
\usepackage{enumitem}
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent

%to crossref between files
%clear both directories
%pdflatex manuscript first
%pdflatex this file next
%filename does not require extension here
\usepackage{xr}
\externaldocument{path/to/marked/manuscript/filename} %crossref through aux file

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag

\makeatletter %make text labels
\newcommand{\labeltext}[3][]{%
    \@bsphack%
    \csname phantomsection\endcsname %in case hyperref is used
    \def\tst{#1}%
    \def\labelmarkup{} %how to markup the label itself
    %\def\refmarkup{\labelmarkup} %How to markup the reference
    \def\refmarkup{}%
    \ifx\tst\empty\def\@currentlabel{\refmarkup{#2}}{\label{#3}}%
    \else\def\@currentlabel{\refmarkup{#1}}{\label{#3}}\fi%
    \@esphack%
    \labelmarkup{#2}% visible printed text.
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
\lhead{\scriptsize Manuscript ID}
\chead{\scriptsize Reviewer N}
\rhead{\scriptsize \today}
\rfoot{\thepage} %move page number to bottom right

\begin{document}

\begin{center}\textbf{Response to Reviewer}\end{center}

\noindent Thank you for the peer review of this manuscript. Each comment was considered carefully. The manuscript has been revised accordingly in the hope that the updated paper is worthy of publication. A detailed response to each comment is provided in this document.

\begin{center}\textbf{Responses to Reviewer Comments}\end{center}

\leftskip0in\relax \rightskip0in\relax
\noindent\textbf{General comments.}\\
\noindent Reviewer comment.  \\

\leftskip.25in\relax \rightskip.25in\relax
\noindent Author response. \\

\noindent Revisions - 
\begin{enumerate}[leftmargin=.5in,rightmargin=.25in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\labeltext{Statement on how authors will revise the manuscript accordingly.}{X-label-name}
\end{enumerate}
\vspace*{\baselineskip}

%how it works
%in marked manuscript, just \ref{X-label-name} (X = Reviewer X), and then the text in \labeltext{} will be referenced

%repeat as needed

\newpage

\leftskip0in\relax \rightskip0in\relax
\noindent\textbf{Editorial comments.}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item Page X-Line Number N - Abstract 1 - \labeltext{Reviewer editorial comment}{X-ed1}\\
        Author response 
        \vspace{.1in}
    \item Page X-Line Number N - \labeltext{Reviewer editorial comment}{X-ed2}\\
        Author response 
        \vspace{.1in}

    %repeat as needed

\end{enumerate}

\end{document}

### 2020-12-02 peer-reviewer/peer-reviewer.tex
reload

%@TheDoctorRAB
%statement of work
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{caption}
\captionsetup[table]{skip=11pt} %sets a space after table caption
\usepackage{times}
\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent
\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations
\usepackage{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}

%\usepackage{xr} %document crossreferencing
%\externaldocument{/path/to/auxfilename} %aux file needed

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag

\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %turn off line in header
\lhead{\scriptsize Funding Agency}
\chead{\scriptsize Statement of Work - \textit{Name}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

@@

\begin{center}{\textbf{Specific funding call}}
\end{center}

\begin{center}{\textbf{Proposal Title}}\end{center}

    \begin{center}{Name (co-PI) or (PI)\\University $\sq$ Department}
\end{center}

\noindent Prof./Dr. LastName will collaborate/partner/join (list team just as institutions or people if you prefer)...introductory statement of what proposal will do.\\

\noindent\textbf{Work will include - }
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item As 
    \item many
    \item as
    \item needed
    \item ! 
\end{enumerate}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{caption}
\captionsetup[table]{skip=11pt} %sets a space after table caption
\usepackage{times}
\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent
\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations
\usepackage{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}
\usepackage{hyperref}

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\renewcommand\labelenumi{(\theenumi)} %changes 1. to (1) in enumerated list

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
\renewcommand{\headrulewidth}{0.5pt} %turn off line in header
\lhead{\scriptsize ID}
\chead{\scriptsize Peer review - \textit{Authors(s)}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

@@

\begin{titlepage}
    \title{
        Title\\
    }
    \author{
        Name
        \\ \\ \\
        Affiliation 
        \\ \\
        Submitted to: \textit{Journal Name}\\[ID]
        \\ \\ \\
        editor 
    }
\clearpage %not have page number on title page
\maketitle
\thispagestyle{empty} %start with page number 1 on second page
\end{titlepage}

\noindent\textbf{Preface.}

\noindent\textbf{General comments.}

\noindent\textbf{Section comments.}

\noindent\textbf{Line items.}
\begin{enumerate}[leftmargin=*]
\end{enumerate}

### 2020-12-02 research-cv/abbreviated-research-two-page-cv.tex
reload

%Research CV template for academics and researchers
%@TheDoctorRAB
\documentclass[letter,oneside,english,10pt,headinclude,headsepline]{amsart}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{bold-extra}
\usepackage{bibentry}
\usepackage{filecontents}
\usepackage[yyyymmdd]{datetime} %set preferred date format
\renewcommand{\dateseparator}{.} %set preferred date separator

@@

\usepackage{fancyhdr} 
\pagestyle{fancy}
\fancyhf{} %page number on bottom right
\lhead{\scriptsize Title Name} %title and name
\chead{\scriptsize \textit{Vita}} %maybe something more specific here if desired
\rhead{\scriptsize \today} %date
\rfoot{\thepage} %page number

@@

%peer reviewed journal papers
\begin{filecontents}{peer-reviewed.bib} 
    @article{
        pr1,
        author = {},
        journal = {},
        pages = {},
        title = {{}},
        volume = {},
        year = {}
    }
\end{filecontents}

%books and book contributions
\begin{filecontents}{book-contribution.bib}
    @book{
        bk1,
        author = {},
        title = {{}},
        year = {},
        publisher = {{}}
        isbn = {}
    }
\end{filecontents}

%conference proceedings
\begin{filecontents}{conference-proceedings.bib}
    @conference{
        cf1,
        author = {},
        title = {{}},
        year = {},
        organization = {},
        address = {}
    }
\end{filecontents}

%reports, misc, non-refeered
\begin{filecontents}{reports.bib}
    @misc{
        rp1,
        author = {},
        title = {{}},
        institution = {},
        year = {}
    }
\end{filecontents}

%conference presentations - not the same as invited talks 
\begin{filecontents}{conference-presentations.bib}
    @conference{
        cf1,
        author = {},
        title = {{}},
        year = {},
        organization = {},
        address = {}
    }
\end{filecontents}

@@

%.bib files to create
\nobibliography{peer-reviewed,book-contribution,conference-proceedings,reports,conference-presentations}

%.bst file
\bibliographystyle{} %custom bst file

@@

\begin{center}{
        \textsc{ %block caps font
            \textbf{
                Name\\
                {\footnotesize Title} \\
                {\footnotesize Institution $\sq$ Department} \\
                {\footnotesize Address} \\
                {\footnotesize email $\sq$ twitter $\sq$ phone} 
            }
        }
    }
\end{center}

@@

\section*{Education}
\noindent\textbf{University}\\
\textbf{Doctor of Philosophy $\sq$ Major} \hfill{\textit{Date}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Dissertation: }
    \item[]Examination fields: 
    \item[]Committee: 
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University}\\
\textbf{Master of Science $\sq$ Major} \hfill{\textit{Date}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Thesis: }
    \item[]Advisor: 
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textbf{University}\\
\textbf{Bachelor of Science $\sq$ Major and distinction(s)} \hfill{\textit{}}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Capstone: }
    \item[] Advisor: 
\end{itemize}

\section*{Research Experience} %academic positions
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary 
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary

\section*{Related Research Experience} %like internships
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary 
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary

\section*{Related Professional Experience} %anything else
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary 
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title} \hfill{\textit{From - To}}\\
Brief summary

\section*{Awarded Projects} %chronologically
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{enumerate}

\section*{Thesis Committees}
\subsection*{Major Professor} %or adviser, whatever the official title is
\noindent\textit{Current}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Student Name, Degree - Topic
\end{itemize}
\vspace*{.75\baselineskip}

\noindent\textit{Graduates}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Student Name, Degree - Thesis Title 
\end{itemize}

\subsection*{Member}
\noindent\textit{Graduates}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Student Name, Degree - Thesis Title 
\end{itemize}

\section*{Refereed Journal Publications}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{pr1}.
\end{enumerate}

\section*{Book Contribution}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{bk1}.
\end{enumerate}

\section*{Refereed Conference Proceedings}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{cf1}.
\end{enumerate}

\section*{Non-Refereed Technical Reports}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{rp1}.
\end{enumerate}

\section*{Conference Presentations}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.15ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{cf1}.
\end{enumerate}

\section*{Teaching Experience}
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title}\\ 
\textit{Course Number: Title \hfill{Semester}}\\
Summary
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title}\\ 
\textit{Course Number: Title \hfill{Semester}}\\
Summary

\section*{Related Teaching Experience} %for TA, etc.
\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title}\\ 
\textit{Course Number: Title \hfill{Semester}}\\
Summary
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution $\sq$ Location $\sq$ Department}\\
\textbf{Title}\\ 
\textit{Course Number: Title \hfill{Semester}}\\
Summary

\section*{Professional Service} 
\subsection*{University/Institution} %department/college related activities
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Academic Search Committees}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Year}
    \item[]Search committee %don't say it was a failed search 
            \vspace{.05in}
    \item[]\textit{Year}
    \item[]Search committee %don't say it was a failed search 
\end{itemize}

\subsection*{Peer Reviewer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Regular periods} %for journals/conferences on a regular basis
    \item[] 
            \vspace{.05in}
    \item[]\textit{Year} %specific one-time reviewing
    \item[] 
            \vspace{.05in}
    \item[]\textit{Year} %specific one-time reviewing
    \item[] 
\end{itemize}

\subsection*{Conference Committees}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Technical Session Organizer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Technical Session Chair}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Symposia Organizer}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item[]
\end{itemize}

\subsection*{Invited Talks}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{University/Institution $\sq$ Department} %speaking at graduate orientation, etc.
    \item[]Title $\sq$ Purpose \hfill{\textit{Dates}}
        \vspace{.05in}
    \item[]\textit{Seminars} %typical department seminar talks
    \item[]University/Institution Department \hfill{\textit{Date}}
        \vspace{.05in}
    \item[]\textit{Lightning Talks} %throw everything in there 
    \item[]Talk \hfill{\textit{Date}}
        \vspace{.05in}
    \item[]\textit{Outreach}
    \item[]Event \hfill{\textit{Date}}
        \vspace{.05in}
    \item[]\textit{Lectures} %invited to lecture in a course
    \item[]University/Institution - Course or topic \hfill{\textit{Date}}
\end{itemize}

\subsection*{Community Service}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textit{Event} \hfill{\textit{Date}}
    \item[]Summary 
        \vspace{.05in}
    \item[]\textit{Event} \hfill{\textit{Date}}
    \item[]Summary 
\end{itemize}

\subsection*{Outreach and Related Professional Activities} %career fairs, etc.
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Event \hfill{\textit{Date}}
\end{itemize}

\subsection*{Professional Training}
\noindent\textbf{University/Institution}\\
\textbf{Role}\\
\textit{Title of Event} \hfill{\textit{Date}}\\
Summary
\vspace*{.75\baselineskip}

\noindent\textbf{University/Institution}\\
\textbf{Role}\\
\textit{Title of Event} \hfill{\textit{Date}}\\
Summary

\subsection*{Awards and Fellowships}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textbf{University/Institution}
    \item[]Award or fellowship \hfill{\textit{Date}}
        \vspace{.05in}
    \item[]\textbf{University/Institution}
    \item[]Award or fellowship \hfill{\textit{Date}}

\subsection*{Professional Societies and Positions}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]\textbf{Society}
    \item[]Position \hfill{\textit{From - To}}
        \vspace{.05in}
    \item[]\textbf{Society}
    \item[]Position \hfill{\textit{From - To}}
\end{itemize}

>>>>

%@TheDoctorRAB
\documentclass[letter,oneside,english,10pt,headinclude,headsepline]{amsart}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{bold-extra}
\usepackage{bibentry}
\usepackage{filecontents}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{.}

@@

\usepackage{fancyhdr} 
\pagestyle{fancy}
\fancyhf{} %page number on bottom right
\lhead{\scriptsize Title Name}
\chead{\scriptsize \textit{Abbrv. Vita}}
\rhead{\scriptsize \today} %date
\rfoot{\thepage} %page number

@@

%\natexlab not working - remove from bbl file
\begin{filecontents}{peer-reviewed.bib} 
    @article{
        pr1,
        author = {},
        journal = {},
        pages = {},
        title = {{}},
        volume = {},
        year = {}
    }
\end{filecontents}

@@

\nobibliography{peer-reviewed} %bib file
\bibliographystyle{standard} %custom bst file

@@

{\centering 
        \textsc{ %block caps font
            \textbf{
                Name $\sq$ Title \\
                University/Institution $\sq$ Department \\
                Address 1 $\sq$ Address 2\\
                email $\sq$ @Twitter $\sq$ office phone 
            }
        }
\par}

@@

\subsection*{Education and Training}
\noindent University $\sq$ Doctor of Philosophy $\sq$ Major \hfill{Date}\\
University $\sq$ Master of Science $\sq$ Major \hfill{Date}\\
University $\sq$ Bachelor of Science $\sq$ Major \hfill{Date}

\subsection*{Research and Professional Experience}
\noindent University $\sq$ Location $\sq$ Department
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Title/Position \hfill{From - To}
\end{itemize}
\vspace*{.5\baselineskip}

\noindent University $\sq$ Location $\sq$ Department
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]Title/Position \hfill{From - To}
\end{itemize}

\subsection*{Awarded Projects} %chronologically
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{enumerate}

\subsection*{Relevant Publications\hfill{*students}} 
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=.05ex,partopsep=1ex,parsep=1ex]
    \item\bibentry{pr1}.
\end{enumerate}

\subsection*{Relevant Courses Taught}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[]University $\sq$ Location $\sq$ Department 
    \item[] Course Number: Title 
        \vspace{.05in}
    \item[]University $\sq$ Location $\sq$ Department 
    \item[] Course Number: Title 
\end{itemize}

\subsection*{Synergistic Activities}
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
    \item
    \item
\end{enumerate}
